---
title: "R Notebook"
output: html_notebook
---

In this homework we’ll use the msleep data set provided in the ggplot package.
It concerns the sleeping patterns of various types of mammal.
```{r}
library(tidyverse)
library(WebPower)
```

Explore the dataset, familiarise yourself with it.
```{r}
msleep
```

Jabberwockies sleep for around 7 hours a night, on average. Perform an 
appropriate statistical test to determine whether the mean sleep_total in the
sampled population of animal types differs from the typical value for
jabberwockies.
```{r}
# Ho = mean sleep for jaberwockies - mean sleep for all other animals == 0
# Ha = mean sleep for jaberwockies - mean sleep for all other animals != 0

t.test(x = msleep$sleep_total, mu = 7, alternative = "two.sided")
# p value < 0.05 so can reject Ho
```

Perform an appropriate statistical test to determine whether omnivores sleep for
significantly longer than herbivores, on average.
```{r}
# Ho = mean sleep omnivores - mean sleep herbivores == 0
# Ha = mean sleep omnivores - mean sleep herbivores > 0

herb <- msleep[msleep$vore == "herbi", ]
omni <- msleep[msleep$vore == "omni", ]

t.test(x = herb$sleep_total, y = omni$sleep_total, alternative = "less", paired = FALSE)
# p value > 0.05 means no significant difference in sleep_total
```

Perform an appropriate statistical test to determine whether the proportion of 
domesticated animals in the population of animal types is greater than 5%
```{r}
# Ho = proportion of deomesticated animals <= 5%
# Ha = proportion of deomesticated animals > 5%

num_domesticated <- msleep %>%
        filter(conservation == "domesticated")

# Success criteria
0.05 * nrow(msleep) >= 10
(1 - 0.05) * nrow(msleep) >= 10

binom.test(x = nrow(num_domesticated), n = nrow(msleep), p = 0.05, alternative = "greater")
# p value < 0.05 so can reject Ho
```

Determine an appropriate sample size for the following problem:

A quality analyst wants to estimate a 99% confidence interval to within ±0.01g 
for the mean weight of fruit pastels produced by a production line tomorrow.
Prior evidence suggests the standard deviation in fruit pastel weights is 0.05g

What is the minimum number of fruit pastels the analyst should sample?
```{r}
CI <- 0.995
interval <- 0.01
sd <- 0.05

(qnorm(CI)^2 * sd^2) / interval^2
# 166 fruit pastilles
```

Determine an appropriate sample size for the following problem:

A clinical dietician wants to compare two different diets, A and B, for diabetic
patients. She hypothesizes that diet A (Group 1) will be different from diet B 
(Group 2), in terms of mean blood glucose. She plans to get a random sample of
diabetic patients and randomly assign them to one of the two diets. At the end 
of the experiment, which lasts 6 weeks, a fasting blood glucose test will be 
conducted on each patient. She also expects that the average difference in blood
glucose measure between the two group will be about 10 mg/dl. Furthermore, she
also assumes the standard deviation of blood glucose distribution for diet A to 
be 15 mg/dl and the standard deviation for diet B to be 17 mg/dl. The dietician
wants to know the number of subjects needed in each group assuming equal sized 
groups.
```{r}
pooled_sd <- sqrt((15^2 + 17^2) / 2)

effect_size <- 10 / pooled_sd
        
wp.t(n1 = NULL, d = effect_size, alpha = 0.05, power = 0.8,
        type = "two.sample", alternative = "two.sided")
# at least 42 in each group if equal size
```

What would the power of the test above be if the number of patients in each 
group was 100?
```{r}
wp.t(n1 = 100, d = effect_size, alpha = 0.05, power = NULL,
        type = "two.sample", alternative = "two.sided")
# 99%
```
