---
title: "R Notebook"
output: html_notebook
---

1.1
createdb wrestling
psql -d wrestling -f ~/de1_classnotes/week_02/day_2/7_homework/wrestling.sql

Get user details from keyring
```{r}
library(keyring)
keyring_unlock(keyring = "local")
username <- key_get("postgresql_username", keyring = "local")
password <- key_get("postgresql_password", keyring = "local")
keyring_lock(keyring = "local")
```

Create a connection to the local wrestling database from R. 
```{r}
library(RPostgreSQL)

my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = username,
        password = password, dbname = "wrestling", host = "localhost")
```

Using the R connection you just created, write and execute a SQL query to return
all the wrestlers in the wrestlers table.
```{r}
dbGetQuery(my_db_connection, "SELECT * FROM wrestlers")
```

State which data type you think each column stores:
born          - varchar
name          - varchar
gender        - varchar
win_percent   - double
total_matches - int

1.2
Store the credentials in appropriately named keys in the remote keyring.
```{r}
#keyring_create(keyring = "remote")
#key_set(service = "elephant_username", keyring = "remote")
#key_set(service = "elephant_password", keyring = "remote")
#keyring_lock(keyring = "remote")
```

```{r}
keyring_unlock(keyring = "remote")
elephant_username <- key_get("elephant_username", keyring = "remote")
elephant_password <- key_get("elephant_password", keyring = "remote")
keyring_lock(keyring = "local")
```

Use your credentials to establish a connection from R to the remote database.
```{r}
my_remote_connection <- dbConnect(drv = PostgreSQL(max.con = 2), 
        user = elephant_username, password = elephant_password,
        dbname = "mvhbdgdk", host = "manny.db.elephantsql.com")
```

Using this R connection, write and execute a query to return all the wrestlers
from the wrestlers table
```{r}
dbGetQuery(my_remote_connection, "SELECT * FROM wrestlers")
```

2
Return all the details for any wrestlers from the United Kingdom
```{r}
dbGetQuery(my_db_connection, "SELECT * FROM wrestlers WHERE born = 'United Kingdom'")
```

Get the names of all Japanese wrestlers who have appeared in 40 or more matches.
```{r}
dbGetQuery(my_db_connection, 
        "SELECT *
         FROM wrestlers 
         WHERE born = 'Japan' AND total_matches > 40"
)
```

Find the wrestlers who have won between 50% and 60% of their matches.
```{r}
dbGetQuery(my_db_connection,
        "SELECT *
         FROM wrestlers
         WHERE win_percent BETWEEN 50 AND 60"
)
```

Find all the wrestlers with names beginning with ‘X’.
```{r}
dbGetQuery(my_db_connection,
        "SELECT *
         FROM wrestlers
         WHERE name LIKE 'X%'"
)
```

Find all the wrestlers who were born in countries beginning with the letter ‘I’. Try this using IN (there are 9 countries) and using a wildcard comparison.
```{r}
dbGetQuery(my_db_connection,
        "SELECT *
         FROM wrestlers
         WHERE born IN ('India', 'Iran', 'Ireland', 'Italy')"
)

dbGetQuery(my_db_connection,
        "SELECT *
         FROM wrestlers
         WHERE born LIKE 'I%'"
)
```

Find all the wrestlers who were not born in countries beginning with the letter ‘I’.
```{r}
dbGetQuery(my_db_connection,
        "SELECT *
         FROM wrestlers
         WHERE born NOT LIKE 'I%'"
)
```

Close connections
```{r}
dbDisconnect(conn = my_db_connection)
dbDisconnect(conn = my_remote_connection)
```









