---
title: "R Notebook"
output: html_notebook
---

```{r, message = FALSE}
library(tidyverse)
library(outliers)
library(lubridate)
library(mice)
```

Load in the women_in_gov csv file. Make sure you remove all metadata from the
top.
```{r, message = FALSE}
women_in_gov <- 
        read_csv("~/de1_classnotes/week_07/day_1/5_cleaning_data_homework/data/women_in_gov.csv",
                skip = 4)
```

Some of the column names contain spaces and numbers. Fix the column names using 
the make.names function.
```{r}
names(women_in_gov) <- make.names(names(women_in_gov))
```

We have some columns in the data that don’t really need to be there. Confirm 
that the X64, Indicator.Name and Indicator.Code have the same values for all 
observations. If they do, remove those columns.
```{r}
unique(women_in_gov$X64)
unique(women_in_gov$Indicator.Name)
unique(women_in_gov$Indicator.Code)

women_in_gov <- women_in_gov %>%
        select(-c(X64, Indicator.Name, Indicator.Code))
```

Now we have got rid of the extra columns, we can rename the remaining country
columns to something more tidy. Rename the Country.Name and Country.Code 
variables to country and code.
```{r}
colnames(women_in_gov)[colnames(women_in_gov) == "Country.Name"] <- "country"
colnames(women_in_gov)[colnames(women_in_gov) == "Country.Code"] <- "code"
```

Think back to last week where we talked about wide vs long format. As the data 
is in wide format, it’s pretty clear to see we have a lot of missing values. 
Reshape the data from wide to long format, so that for each country the year 
column becomes a row.
```{r}
women_in_gov_long <- gather(women_in_gov, key = year, value = prop_women, X1960:X2018)
```

You’ll notice your prop_women column contains missing values. Let’s do a few 
things. First, let’s count how many missing values you have. Then check how many
different missing values you have (e.g. how many unique ones do you have). Then
decide how you will impute. Will you insert average imputation values, most 
common imputation values, or use the multiple imputation method? Explain your
decision. Then fix the missing values.
```{r}
sum(is.na(women_in_gov_long$prop_women))

women_in_gov_long <- women_in_gov_long %>%
        separate(col = year, into = c("prefix", "year_recorded"), sep = "X",  remove = TRUE) %>%
        select(-prefix) %>%
        filter(year_recorded >= 1990)
```

```{r}
md.pattern(women_in_gov_long)

women_imputed <- mice(women_in_gov_long, m = 5, maxit = 50, method = 'pmm')
```

```{r}
complete_women <- complete(women_imputed, 2)
```

Create a boxplot to see if there are any outliers in the proportion of women.
```{r}
ggplot(complete_women) +
        aes(y = prop_women) +
        geom_boxplot()
```

Use the outliers package to calculate a zscore for each observation in your 
data. Mark any of the values in the prop_women column that are more or less than
3 standard deviations above or below the mean as outliers. Add this outlier flag
as a new column within the dataset. Create a table that only contains the 
outliers and have a look at them.
```{r}
measurement_score <- scores(complete_women$prop_women)
is_outlier <- measurement_score > 3 | measurement_score < -3

complete_women$is_outlier <- is_outlier

women_outliers <- complete_women %>%
        filter(is_outlier == TRUE)
```

Next decide - what will you do with these outliers? Create a table with your 
newly dealt with outliers.
- doing nothing with the outliers,  could be valid data
```{r}
complete_women
```

Extension task

We will be looking for outliers and relationships between the 
receipt_description variable and the receipt_value variable. Load in the data.
Check the variable names, and check for missing values in the variable of
interest receipt_value.
```{r}
deputies_info <- 
        read_csv("~/de1_classnotes/week_07/day_1/5_cleaning_data_homework/data/deputies_info.csv")

names(deputies_info)
sum(is.na(deputies_info$receipt_value))
```

Spend some time visualizing any outliers in the receipt_value column. Does it 
have a relationship with the receipt_description column?
```{r}
ggplot(deputies_info) +
        aes(x = receipt_description, y = receipt_value) +
        geom_boxplot() +
        coord_flip()
```

Identify which rows in the receipt_value column of data_v1 dataset are outliers.
Try plotting them or looking through just the outliers.

Calculate the outlier zcores for the receipt_value column. Replot the data, and 
then remove the outliers.
```{r}
measurement_score <- scores(deputies_info$receipt_value)
is_outlier <- measurement_score > 3 | measurement_score < -3

deputies_info$is_outlier <- is_outlier

deputies_outliers <- deputies_info %>%
        filter(is_outlier == TRUE)

ggplot(deputies_outliers) +
        aes(x = receipt_description, y = receipt_value) +
        geom_boxplot() +
        coord_flip()
```
