---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(dbplyr)
library(lubridate)
library(RSQLite)
library(DBI)
```

```{r}
date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")

mammals <- dbConnect(SQLite(), "~/de1_classnotes/week_06/day_2/5_homework/mammals.sqlite")

plots   <- tbl(mammals, sql("SELECT * FROM plots"))
species <- tbl(mammals, sql("SELECT * FROM species"))
surveys <- tbl(mammals, sql("SELECT * FROM surveys"))
```

MVP

Extract the different components (year, month, mday, yday, wday) from the 
variable date1. Add the labels to the month and do not abbreviate the month 
labels.
```{r}
year(date1)
month(date1, label = TRUE, abbr = FALSE)
mday(date1)
yday(date1)
wday(date1)
```

Add 14 days to your date1 variable and store it in a variable called 
next_fortnight. Take away 10 years from your date2 variable, and store it in
previous_decade.
```{r}
next_fortnight <- date1 + weeks(2)
previous_decade <- next_fortnight - years(2)
```

Create a variable called this_year which contains today’s date. Then create an
interval object which uses this_year and the previous_decade variable you made
above. Store it in interval_years.
```{r}
this_year <- today()
interval_years <- interval(this_year, previous_decade)
```

Change the time zone of both your date variables to “America/New_York”, and call
them nyc_date1 and nyc_date2.
```{r}
nyc_date1 <- with_tz(date1, tzone = "America/New_York")
nyc_date2 <- with_tz(date2, tzone = "America/New_York")
```

Let’s move on to using the data from our database.

Create a tibble called survey_tibble. Use the make_datetime function to create a
new column within that tibble called full_date. 
```{r}
survey_tibble <- surveys %>%
        collect() %>%
        mutate(full_date = make_datetime(year = 2019L, month = 8L, day = 6L))
```

Check what type the new full_date variable is.
```{r}
class(survey_tibble$full_date)
```

Convert the sex variable within survey_tibble to a logical variable. Save it in
surveyor_sex.
```{r}
survey_tibble <- survey_tibble %>%
        mutate(surveyor_sex = sex == "M")
```

Using the dbplyr package, join the species and surveys table, so that only those
species who were surveyed are kept. Save it in a new tibble called all_species.
```{r}
all_species <- inner_join(surveys, species, by = "species_id")
```

Using the dpblyr package, implement a query (in R) that joins the species and
survey tables together, and that returns the number of birds observed in each
plot, each year. 
```{r}
all_species %>%
        filter(taxa == "Bird") %>%
        group_by(year) %>%
        summarise(count = n())
```

What would the equivalent query be in SQL?
```{r, eval = FALSE}
SELECT su.year
        , COUNT(su.id)
FROM surveys AS su
        JOIN species AS sp ON su.species_id = sp.species_id
WHERE sp.taxa = "Bird"
GROUP BY su.year
```

Extensions

```{r}
library(nycflights13)
```

Make a date-time column called departure_date from the year, month, day, hour, 
and minute variables in the flights tibble.
```{r}
flights <- flights %>%
        mutate(departure_date = ymd_hm(paste0(year, "-", month, "-", day, " ", hour, ":", minute)))
```

Add the weather to the flights data by city of origin.
```{r}
flights <- inner_join(
        flights, 
        weather, 
        by = c("origin" = "origin", "time_hour" = "time_hour")
)
```

```{r}
flights
airports[ , c("faa", "lat", "lon")]
```

Add the location of the origin and destination (i.e. the lat and lon) to 
flights. Only keep those that have a location.
```{r}
inner_join(flights, airports[ , c("faa", "lat", "lon")], by = c("origin" = "faa"))
```

Write a query which shows the mean delay of flights for each tailnumber and 
airline carrier, where the arrival delay was greater than 100 minutes.
```{r}
flights %>%
        filter(arr_delay > 100) %>%
        group_by(tailnum, carrier) %>%
        summarise(mean(arr_delay))
```

Find the 10 most popular destinations to fly to, and then perform a join to find
which flight went with those top 10 destinations.
```{r}
flights %>%
        group_by(dest) %>%
        summarise(count = n()) %>%
        arrange(desc(count)) %>%
        top_n(10) %>%
        inner_join(flights, by = "dest")
```
