---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(GGally)
library(fastDummies)
library(ggiraphExtra)
```

MVP

Load the diamonds.csv data set and undertake an initial exploration of the data.
You will find a description of the meanings of the variables on the relevant 
Kaggle page.
```{r}
diamonds <- read.csv("~/de1_classnotes/week_11/day_1/4_diamonds_hw/diamonds.csv")
glimpse(diamonds)
summary(diamonds)
str(diamonds)
```

We expect the carat of the diamonds to be strong correlated with the physical 
dimensions x, y and z. Use ggpairs() to investigate correlations between these
four variables.
```{r}
diamonds_trim <- diamonds %>%
        select(carat, x, y, z)

ggpairs(diamonds_trim)
```

So, we do find significant correlations. Let’s drop columns x, y and z from the
dataset, in preparation to use only carat going forward.
```{r}
diamonds_trim <- diamonds %>%
        select(-c(X, x, y, z))
```

We are interested in developing a regression model for the price of a diamond in
terms of the possible predictor variables in the dataset.

Use ggpairs() to investigate correlations between price and the predictors (this
may take a while to run, don’t worry, make coffee or something).
```{r}
ggpairs(diamonds_trim)
```

Perform further ggplot visualisations of any significant correlations you find.
```{r}
ggplot(diamonds_trim) +
        aes(x = carat, y = price) +
        geom_point() +
        geom_smooth(method = "lm", se = FALSE) 
```

Shortly we may try a regression fit using one or more of the categorical 
predictors cut, clarity and color, so let’s investigate these predictors:

Investigate the factor levels of these predictors. How many dummy variables do 
you expect for each of them?
```{r}
unique(diamonds_trim$cut)
# 5 levels so 4 dummy variables
unique(diamonds_trim$clarity)
# 8 levels so 7 dummy variables
unique(diamonds_trim$color)
# 7 levels so 6 dummy variables
```

Use the dummy_cols() function in the fastDummies package to generate dummies for
these predictors and check the number of dummies in each case.
```{r}
diamonds_trim <- dummy_cols(diamonds_trim,
                select_columns = c("cut", "clarity", "color"),
                remove_first_dummy = TRUE)
```

Going forward we’ll let R handle dummy variable creation for categorical
predictors in regression fitting (remember lm() will generate the correct 
numbers of dummy levels automatically, absorbing one of the levels into the 
intercept as a reference level)

First, we’ll start with simple linear regression. Regress price on carat and 
check the regression diagnostics.
```{r}
diamond_model <- lm(price ~ carat, data = diamonds_trim)
summary(diamond_model)
plot(diamond_model)
```

Run a regression with one or both of the predictor and response variables log() 
transformed and recheck the diagnostics. Do you see any improvement?
```{r}
diamond_model_log <- lm(price ~ log(carat), data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)

diamond_model_log <- lm(log(price) ~ carat, data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)

diamond_model_log <- lm(log(price) ~ log(carat), data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)
```

Let’s use log() transformations of both predictor and response. Next, experiment
with adding a single categorical predictor into the model. Which categorical 
predictor is best? [Hint - investigate r2 values]
```{r}
diamond_model_log <- lm(log(price) ~ log(carat) + cut, data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)

diamond_model_log <- lm(log(price) ~ log(carat) + clarity, data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)

diamond_model_log <- lm(log(price) ~ log(carat) + color, data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)

# clarity appears to be the best (highest r squared).
```

Interpret the fitted coefficients for the levels of your chosen categorical 
predictor. Which level is the reference level? Which level shows the greatest
difference in price from the reference level? [Hints - remember we are 
regressing the log(price) here, and think about what the presence of the 
log(carat) predictor implies. We’re not expecting a mathematical explanation]
```{r}
# I1 is reference level
# IF shows greatest difference in coefficient.
# - difference between IF and I1 is the exponential of the coefficient
# - exp(1.114625) = 3.048425
```

Extension

Try adding an interaction between log(carat) and your chosen categorical 
predictor. Do you think this interaction term is statistically justified?
```{r}
diamond_model_log <- lm(log(price) ~ log(carat) + clarity + log(carat):clarity,
        data = diamonds_trim)
plot(diamond_model_log)
summary(diamond_model_log)
```

Find and plot an appropriate visualisation to show the effect of this
interaction
```{r}
ggplot(diamonds_trim) +
        aes(x = log(carat), y = log(price), colour = clarity) +
        geom_point(alpha = 0.1) +
        geom_smooth(method = "lm", se = FALSE) +
        facet_wrap(~ clarity)
```

