---
title: "Week 01 Day 02 Homework"
output: html_notebook
---

Part 1:

Create a vector called stock_prices with the following data points: 23, 27, 23, 21, 34, 24, 25, 30, 37, 30.

```{r}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
```

Create a vector called day_of_week, which repeats Monday to Friday twice. i.e. ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’, ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’.

```{r}
day_of_week <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
```

Create a vector called day_of_week_factor, which has the same data as day_of_week, but as a factor.

```{r}
day_of_week_factor <- factor(day_of_week)
```

Created a vector called named_stock_prices, which is stock prices, named with days of the week.

```{r}
named_stock_prices <- stock_prices
names(named_stock_prices) <- day_of_week
```

Make a data frame called stock_data with the stock price and day of the week information in it, and View the result.

```{r}
stock_data <- data.frame(stock_price = named_stock_prices, day_of_week = names(named_stock_prices))
stock_data
```

Make a matrix called stock_matrix with 2 columns and 5 rows, so that the stock prices for one week are the first column, and the stock prices for the second week are the second column.

```{r}
stock_matrix <- matrix(stock_prices, nrow = 5, ncol = 2)
```

Make a list called stock_list with named elements, that has the individual vectors of stock_prices and day_of_week along with the matrix you made in question 4.

```{r}
stock_list <- list(stock_prices = stock_prices, day_of_week = day_of_week, stock_matrix = stock_matrix)
```

Part 2:

Select the 4th, 5th and 6th stock prices from stock_prices.

```{r}
stock_prices[4:6]
```

Select the stock prices greater than 30 from stock_prices.

```{r}
stock_prices[(stock_prices > 30)]
```

Select the day_of_week column from the stock_data data frame.

```{r}
stock_data[, "day_of_week",  drop = FALSE]
```

Select the rows of the stock_data data frame where the stock_prices is less than 25.

```{r}
stock_data[stock_prices < 25, ]
```

Select the 1st column of the matrix

```{r}
stock_matrix[ , 1]
```

Select the 3rd row of the matrix

```{r}
stock_matrix[3, ]
```

Select the 3rd element in the 1st row of the matrix

```{r}
stock_matrix[3, 1]
```

Select the matrix stock_matrix from stock_list.

```{r}
stock_list["stock_matrix"]
```

Part 3:

Download the tidyquant library.

```{r}
install.packages("tidyquant")
library(tidyquant)
```

Use it to get stock prices from a company of your choice from the current year. You’ll need to look up the help file to do this.

```{r}
msft <- tq_get("MSFT", get = "stock.prices", from = "2019-01-01")
```


Edit the data frame so only columns are date and closing.

```{r}
msft <- msft[ , c("date", "close")]
```

Subset to find the rows where closing price is higher than average.

```{r}
msft[(msft$close > (mean(msft$close))), ]
```





