---
title: "R Notebook"
output: html_notebook
---

Create at least one plot for each sheet in the dataset.
Use a variety of different plot types.
Add labels to make the plots stand on their own.
Use a consistent colour scheme throughout the plots

Display the same data in multiple ways, for at least some of the datasets
Create your own theme and use it consistently throughout the data.
Use some of our ggplot2 extensions.

Load libraries needed
```{r}
library(readxl)
library(ggplot2)
library(ggwordcloud)
```

Read data in
```{r}
filename <- "~/de1_classnotes/week_05/day_5/4_weekend_homework/green_bindle_consulting.xlsx"

sheets <- excel_sheets(filename)

full_list <- lapply(sheets, function(x) { read_excel(filename, sheet = x) })
```

Create a colour scheme and theme
```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

my_theme <- function(size = 12) {
        theme_minimal() %+replace%
        theme(
                panel.background = element_blank(),
                plot.title = element_text(size = size + 2, hjust = 0),
                legend.text = element_text(size = size - 4),
                axis.text = element_text(size = size - 4),
                axis.title = element_text(size = size),
        )
}
```

Data1
```{r}
ggplot(as.data.frame(full_list[1])) +
        aes(x = Year, y = Value, fill = Item) +
        geom_bar(stat = "identity", position = "dodge") +
        labs(
                title = "Value of various Items by Year",
                subtitle = "Assets and Liabilities of Green-Bindle Consulting LLP\n",
                x = "\nYear",
                y = "Value\n"
        ) +
        scale_fill_manual(values = col_scheme) +
        my_theme()
```

```{r}
ggplot(as.data.frame(full_list[1])) +
        aes(x = Year, y = Value, colour = Item) +
        geom_line() +
        labs(
                title = "Value of various Items by Year",
                subtitle = "Assets and Liabilities of Green-Bindle Consulting LLP\n",
                x = "\nYear",
                y = "Value\n"
        ) +
        scale_colour_manual(values = col_scheme) +
        my_theme()
```

Data2
```{r}
ggplot(as.data.frame(full_list[2])) +
        aes(x = Year, y = Value, fill = Status) +
        geom_bar(stat = "identity", position = "dodge") +
        labs(
                title = "Value of Statuses by Year",
                subtitle = "Green-Bindle Consulting LLP\n",
                x = "\nYear",
                y = "Status\n"
        ) +
        scale_fill_manual(values = col_scheme) +
        my_theme()
```

Data3
```{r}
data3 <- as.data.frame(full_list[3])

data3$Item <- factor(data3$Item, levels = rev(data3$Item))

ggplot(data3) +
        aes(x = Item, y = Value, fill = Value) +
        geom_bar(stat = "identity") +
        labs(
                title = "Account Balance",
                subtitle = "Credits/Debits to Green-Bindle Consulting LLP\n",
                x = "Item\n",
                y = "\nValue"
        ) +
        scale_fill_gradient(low = "#B6A7B5", high = "#E89FE9") +
        coord_flip() +
        my_theme()
```

Data4
```{r}
ggplot(as.data.frame(full_list[4])) +
        aes(x = Date, y = Allocation, fill = Region) +
        geom_bar(stat = "identity") +
        facet_wrap(~ Purpose + Asset_Class) +
        labs(
                title = "Allocations per Date by Region for different Purposes and Asset Classes",
                subtitle = "Green-Bindle Consulting LLP\n",
                x = "\nDate",
                y = "Allocation\n"
        ) +
        scale_fill_manual(values = col_scheme) +
        my_theme()
```

Data5
```{r}
ggplot(as.data.frame(full_list[5])) +
        aes(x = Item, y = TPs, fill = Basis) +
        geom_bar(stat = "identity") +
        labs(
                title = "Allocations for different Basis per Asset Class",
                subtitle = "Green-Bindle Consulting LLP\n",
                x = "\nItem",
                y = "TPs\n"
        ) +
        scale_fill_manual(values = col_scheme) +
        my_theme()
```

Data6
```{r}
ggplot(as.data.frame(full_list[6])) +
        aes(x = Scenario, y = Balance, colour = Balance) +
        geom_point() +
        labs(
                title = "Balance vs a range of possible scenarios",
                subtitle = "Green-Bindle Consulting LLP\n",
                x = "\nScenario",
                y = "Balance\n"
        ) +
        scale_color_gradient(low = "#B6A7B5", high = "#E89FE9") +
        my_theme()
```

Data7
```{r}
ggplot(as.data.frame(full_list[7])) +
        aes(x = Year, y = Cashflow, colour = Status) +
        geom_line() +
        labs(
                title = "Value of various Items by Year",
                subtitle = "Assets and Liabilities of Green-Bindle Consulting LLP\n",
                x = "\nYear",
                y = "Cashflow\n"
        ) +
        scale_colour_manual(values = col_scheme) +
        my_theme()
```

Data8
```{r}
ggplot(as.data.frame(full_list[8])) +
        aes(label = Word, size = Size, colour = Size) +
        geom_text_wordcloud() +
        labs(
                title = "Frequency of Words Used By Staff",
                subtitle = " At Green-Bindle Consulting LLP\n",
                caption = "\nSize of word corresponds to freqency"
        ) +
        scale_size_area(max_size = 12) +
        scale_color_gradient(low = "#B6A7B5", high = "#E89FE9") +
        my_theme()
```

```{r}
ggplot(as.data.frame(full_list[8])) +
        aes(x = Word, y = Size, fill = Size) +
        geom_bar(stat = "identity") +
        labs(
                title = "Frequency of Words Used By Staff",
                subtitle = " At Green-Bindle Consulting LLP\n",
                x = "Word",
                y = "Frequency"
        ) +
        coord_flip() +
        scale_fill_gradient(low = "#B6A7B5", high = "#E89FE9") +
        my_theme()
```

