---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(rcompanion)
library(DescTools)
```

MVP

Now we’ll go back to CI creation in the normal fashion. We’ll take the ames data
from the CIs lab earlier today and regard it now as a sample, we won’t be 
drawing any smaller samples from within it. This is the usual situation in an
analysis: you use all the data available to you!

Load the data again and re-familiarise yourself with it
```{r}
ames <- read.csv("ames.csv")
```

Investigate the distribution of Lot.Area. Is the distribution roughly normal? 
If not, what problems do you find?
```{r}
ggplot(ames) +
        aes(x = Lot.Area) +
        geom_histogram()
```

Do you think any problematic features in the distribution of Lot.Area will cause
any difficulties in estimating CIs or performing hypotheses tests using this 
variable?
```{r}
ggplot(ames) +
        aes(y = Lot.Area) +
        geom_boxplot()
# lots of outliers but sample size is high
```

Compute a 95% CI for the mean Lot.Area of the sold houses.
```{r}
groupwiseMean(Lot.Area ~ 1, data = ames, conf = 0.95)
```

You would like to know the mean Lot.Area of the sold houses with higher 
confidence. Calculate the 99% CI for this variable. Is it narrower or broader 
than the 95% CI? Does that make sense?
```{r}
groupwiseMean(Lot.Area ~ 1, data = ames, conf = 0.99)
# broader since we're increasing the confidence
```

Can you split out and show separate 99% CIs for mean Lot.Area grouped by 
House.Style? Do you see any CIs you might not trust?
```{r}
mean_area <- ames %>%
        group_by(House.Style) %>%
        summarise(mean_Lot.Area = mean(Lot.Area))

results_mean <- data.frame()

for (style in levels(ames$House.Style)) {
        style_mean <- groupwiseMean(Lot.Area ~ 1, data = ames[ames$House.Style == style, ], conf = 0.99)
        style_mean <- cbind(style, style_mean)
        
        results_mean <- rbind(results_mean, style_mean)
}
# 2.5Fin only has 8 values

groupwiseMean(Lot.Area ~ House.Style, data = ames, conf = 0.99)
# gives same result as above
```

Calculate a 99% CI for the proportion of houses in the data built before 1890.
Try using the wilson and wald methods. How different are the bounds of the CIs
given by the two methods?
```{r}
ames <- ames %>%
        mutate(old_house = as.factor(ifelse(Year.Built < 1890, "Old", "New")))

obs <- table(ames$old_house)
obs
total <- sum(obs)
total

BinomCI(x = obs, n = total, conf.level = 0.99, method = "wilson")
BinomCI(x = obs, n = total, conf.level = 0.99, method = "wald")
```

[Harder] do a bit of reading on the Wald and Wilson methods. Why do you think
the bounds produced by the two methods are more significantly different when the
proportion is closer to 0? Which method would you choose for the ‘proportion 
before 1890’ CI?
```{r}
# wald is the normal method used in r
# wilson method is trying to correct for extreme proportions (e.g. when one
# value is close to 0.)
```

Calculate 95% CIs for the proportion of total house sales made up by each level 
of House.Style in the data
```{r}
obs <- table(ames$House.Style)

MultinomCI(x = obs, conf.level = 0.95, method = "wilson")
```
