---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(ggplot2)
```

2.1

Again you are going to work with QikBit datasets. They liked the plots that you
produced yesterday, and now want you to polish them by:

- Adding appropriate labels
- Changing the scales and coordinates when appropriate.
- Applying a unified theme, which is described below:

- Graphs should have white backgrounds, and use colour sparingly.
- Font sizes should be ~12pt although titles should be slightly larger and axis
  labels can be slightly smaller.
- All plots should use colours from the following company colour scheme:
```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```

```{r}
ggplot(qb_revenue_breakdown) +
        aes(x = Year, y = Revenue, fill = Product) +
        geom_bar(stat = "identity") +
        scale_y_continuous(labels = scales::comma) +
        scale_fill_manual(values = col_scheme) +
        labs(title = "Revenue per Source by Year\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

```{r}
ggplot(qb_monthly_sales[qb_monthly_sales$Cashflow == "Kwikbit Unit 1 Sales", ]) +
        aes(x = Date, y = Amount) +
        geom_line() +
        scale_colour_manual(values = col_scheme) +
        geom_point() +
        labs(title = "Sales by Date (£)\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

```{r}
ggplot(qb_monthly_sales[qb_monthly_sales$Cashflow != "Kwikbit Unit 1 Sales", ]) +
        aes(x = Date, y = Amount, colour = Cashflow) +
        geom_line() +
        scale_colour_manual(values = col_scheme) +
        scale_y_continuous(labels = scales::comma) +
        labs(title = "Revenue and Costs by Date\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

```{r}
ggplot(qb_competitors) +
        aes(x = Year, y = Revenue, fill = Company) +
        geom_area(alpha = 0.25) +
        scale_fill_manual(values = col_scheme) +
        scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
        labs(title = "Annual Revenue by Company\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

```{r}
ggplot(qb_competitors) +
        aes(x = Year, y = Revenue, colour = Company) +
        geom_line() +
        geom_point() +
        scale_colour_manual(values = col_scheme) +
        scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
        labs(title = "Revenue by Year\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

2.2

Now the company wants to compare the number of steps that their device counts
vs. their competitors. Make a line graph of the number of steps throughout time,
and use faceting to compare between individuals and people. Polish this plot 
like the others.
```{r}
aggregated <- aggregate(qb_device_data[ , -4]$counts,
        by  = list(qb_device_data$device, qb_device_data$id, qb_device_data$hours),
        FUN = sum
)
names(aggregated) <- c("device", "id", "hours", "counts")

aggregated <- aggregated[order(aggregated$device, aggregated$id, aggregated$hours), ]
```

```{r}
ggplot(aggregated) +
        aes(x = hours, y = counts, colour = device) +
        geom_line() +
        facet_wrap(~ id, ncol = 3) +
        scale_colour_manual(values = col_scheme) +
        scale_y_continuous(labels = scales::comma) +
        labs(title = "Hourly step count per user per device\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        )
```

3.

Extend Q2 to include projected sales for the next 3 years on the assumption 
sales increase at 10% pa each year from 1st August. You may assume sales in 
other months can be interpolated (i.e. straight line between Augusts).

You must ensure projections are clearly distinguished from realised sales (e.g.
dotted line used for projections, and a clear legend explaining the 
distinction). Again, make this graph polished according to the companies
specifications.
```{r}
#Question feels too ambiguous to answer. Which plot from part 2/yesterday?
```

The results of our study comparing KwikBit to it’s competitors are proprietary
and we would prefer they were not shared with our competitors. Impose over the 
plot you made in part 2 a transparent piece of text at 15 degrees stating “Not 
for redistribution.”
```{r}
label_position <- data.frame(xpos = 13, ypos = 45000)

ggplot(aggregated) +
        aes(x = hours, y = counts, colour = device) +
        geom_line() +
        facet_wrap(~ id, ncol = 3) +
        scale_colour_manual(values = col_scheme) +
        scale_y_continuous(labels = scales::comma) +
        labs(title = "Hourly step count per user per device\n") +
        theme(
                panel.background = element_rect(fill = "white"),
                plot.title = element_text(size = 14),
                legend.text = element_text(size = 12),
                axis.text = element_text(size = 8),
                axis.title = element_text(size = 12)
        ) +
        geom_text(data = label_position,
                aes(x = xpos, y = ypos, colour = NULL),
                label = "Not for redistribution",
                alpha = 0.4,
                angle = 15,
                show.legend = FALSE
        )
```

