---
title: "R Notebook"
output: html_notebook
---

Load required libraries
```{r}
library(tidyverse)
library(fastDummies)
library(GGally)
library(lubridate)
library(leaps)
```

Read in csv file to dataframe
```{r}
avocado <- read.csv("avocado.csv")
names(avocado) <- tolower(names(avocado))
names(avocado) <- gsub("\\.", "_", names(avocado))
str(avocado)
```

Remove number of avocados total_bags as this can be derived
```{r}
avocado <- avocado %>%
        select(-c(total_bags))
```

Check summary statistics for presence of NAs
```{r}
summary(avocado)
```

Check create a month column and remove date
```{r}
avocado$month <- month(avocado$date)
avocado <- avocado %>%
        select(-c(date))
```

Encode categorical data into dummy columns and then remove.
```{r}
avocado <- dummy_cols(avocado, select_columns = c("type"), remove_first_dummy = TRUE)
avocado <- avocado %>%
        select(-c(x, type))
```

Check which regions we have data for
```{r}
sort(unique(avocado$region))
```

Seems to be an overlap in data collected (e.g.for cities, regions and the whole
of the US) so separate into 3 datasets for each level.
```{r}
areas <- c("GreatLakes", "Midsouth", "Northeast", "NorthernNewEngland", 
        "Plains", "SouthCentral", "Southeast", "West", "WestTexNewMexico")

avocado_areas <- avocado[avocado$region %in% areas, ]
avocado_cities <- avocado[!(avocado$region %in% c(areas, "TotalUS")), ]
avocado_total <- avocado[avocado$region == "TotalUS", ]
```

Exploratory graphs
```{r}
# How does type affect Total Volume for the whole US?
ggplot(avocado_total) +
        aes(x = type_organic, y = total_volume, group = type_organic) +
        geom_boxplot() 

# How does region affect Total Volume per type for each city?
ggplot(avocado_cities) +
        aes(x = region, y = total_volume) +
        geom_bar(stat = "identity") +
        coord_flip() +
        facet_wrap(~ type_organic, ncol = 2)

# Has Volume changed each year overall?
ggplot(avocado_total) +
        aes(x = year, y = total_volume, group = year) +
        geom_boxplot() +
        facet_wrap(~ type_organic, ncol = 1)

# Is there a season change from month to month overall?
ggplot(avocado_total) +
        aes(x = month, y = total_volume, group = month) +
        geom_boxplot() +
        facet_wrap(~ type_organic, ncol = 1)

# How does average price affect overall Total Volume?
ggplot(avocado_total) +
        aes(x = averageprice, y = total_volume) +
        geom_point() +
        facet_wrap(~ type_organic)
```

Seems like the type, region, year, month and average price could all be good 
predictors.

Let's work with area level data.

Remove unused factor levels from dataframe
```{r}
avocado_areas <- droplevels(avocado_areas)
```

Create dummy variables for the regions
```{r}
avocado_areas <- dummy_cols(avocado_areas, select_columns = c("region"), remove_first_dummy = TRUE)
avocado_areas <- avocado_areas %>%
        select(-region)
```

Split into training and test datasets
```{r}
n_data <- nrow(avocado_areas)
test_index <- sample(1:n_data, size = n_data*0.1)

avocado_areas_test  <- slice(avocado_areas, test_index)
avocado_areas_train <- slice(avocado_areas, -test_index)
```

```{r}
model <- regsubsets(total_volume ~ ., data = avocado_areas_train, nvmax = 19, method = "forward")
```

```{r}
summary(model)
plot(model)
```

```{r}
plot(summary(model)$rsq, type = "b")
```

```{r}
summary(model)$which[6, ]
```
