---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(ggiraphExtra)
library(GGally)
```

MVP

You are given a set of data on housing sale prices for the last few years in 
King County (near Seattle) between May 2014 and May 2015. Have a look at the 
variable definitions on the Kaggle page

```{r}
house_prices <- read.csv("~/de1_classnotes/week_11/day_2/4_homework_model_building/kc_house_data.csv")
```

Tidy up the data ready for regression:
- You might like to think about removing some or all of date, id, sqft_living15,
  sqft_lot15 and zipcode (lat and long provide a better measure of location in 
  any event).
```{r}
house_prices <- house_prices %>%
        select(-c("id", "date", "sqft_living15", "sqft_lot15", "zipcode"))
```
  
- Have a think about how to treat waterfront. Should we convert its type?
```{r}
house_prices <- house_prices %>%
        mutate(waterfront = case_when(
                waterfront == 0 ~ FALSE,
                waterfront == 1 ~ TRUE
        ))
```

- We converted yr_renovated into a renovated logical variable, indicating 
  whether the property had ever been renovated. You may wish to do the same.
```{r}
house_prices <- house_prices %>%
        mutate(renovated = case_when(
                yr_renovated == 0 ~ FALSE,
                yr_renovated != 0 ~ TRUE
        )) %>%
        select(-yr_renovated)
```
  
- Have a think about how to treat condition and grade? Are they interval or 
  categorical ordinal data types?
```{r}
house_prices$condition <- factor(house_prices$condition)
house_prices$grade <- factor(house_prices$grade)
```

```{r}
glimpse(house_prices)
```

Check for aliased variables using the alias() function (this takes in a formula
object and a data set). [Hint - formula price ~ . says ‘price varying with all
predictors’, this is a suitable input to alias()]. Remove variables that lead to
an alias.
```{r}
alias(price ~ ., data = house_prices)

house_prices <- house_prices %>%
        select(-sqft_basement)
```

Systematically build a regression model containing up to four main effects 
(remember, a main effect is just a single predictor with coefficient), testing
the regression diagnostics as you go 
- splitting datasets into numeric and non-numeric columns might help ggpairs() 
  run in manageable time, although you will need to add either a price or resid 
  column to the non-numeric dataframe in order to see its correlations with the
  non-numeric predictors.
```{r, message = FALSE}
houses_tidy_numeric <- house_prices %>%
        select_if(is.numeric)

houses_tidy_nonnumeric <- house_prices %>%
        select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_prices$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

First iteration
```{r}
model1a <- lm(price ~ sqft_living, data = house_prices)
summary(model1a)

model1b <- lm(price ~ sqft_above, data = house_prices)
summary(model1b)
```

```{r}
par(mfrow = c(2, 2))
plot(model1a)
plot(model1b)
```

```{r, message = FALSE}
house_prices_residuals <- house_prices %>%
        add_residuals(model1a) %>%
        select(-c("price", "sqft_living"))

houses_tidy_numeric <- house_prices_residuals %>%
        select_if(is.numeric)

houses_tidy_nonnumeric <- house_prices_residuals %>%
        select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_prices$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

Second Iteration
```{r}
model2a <- lm(price ~ sqft_living + lat, data = house_prices)
summary(model2a)

model2b <- lm(price ~ sqft_living + view, data = house_prices)
summary(model2b)
```

```{r}
par(mfrow = c(2, 2))
plot(model2a)
plot(model2b)
```

```{r, message = FALSE}
house_prices_residuals <- house_prices %>%
        add_residuals(model2a) %>%
        select(-c("price", "sqft_living", "lat"))

houses_tidy_numeric <- house_prices_residuals %>%
        select_if(is.numeric)

houses_tidy_nonnumeric <- house_prices_residuals %>%
        select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_prices$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

Third Iteration
```{r}
model3a <- lm(price ~ sqft_living + lat + view, data = house_prices)
summary(model3a)

model3b <- lm(price ~ sqft_living + lat + yr_built, data = house_prices)
summary(model3b)
```

```{r}
par(mfrow = c(2, 2))
plot(model3a)
plot(model3b)
```

```{r, message = FALSE}
house_prices_residuals <- house_prices %>%
        add_residuals(model3a) %>%
        select(-c("price", "sqft_living", "lat", "view"))

houses_tidy_numeric <- house_prices_residuals %>%
        select_if(is.numeric)

houses_tidy_nonnumeric <- house_prices_residuals %>%
        select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_prices$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

Fourth Iteration
```{r}
model4a <- lm(price ~ sqft_living + lat + view + condition, data = house_prices)
summary(model4a)

model4b <- lm(price ~ sqft_living + lat + view + grade, data = house_prices)
summary(model4b)
```

```{r}
par(mfrow = c(2, 2))
plot(model4a)
plot(model4b)
```

```{r}
house_prices_residuals <- house_prices %>%
        add_residuals(model) %>%
        select(-c("price", "sqft_living", "lat", "view", "grade"))

ggpairs(house_prices_residuals, aes(alpha = 0.5))
```

Model 4b has highest r squared.