---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
```

1. If I roll a six-sided dice once, what is the probability of getting a number
   less than 5?
```{r}
dice <- rolldie(1)
less_than_5 <- subset(dice, X1 < 5)
nrow(less_than_5) / nrow(dice)

#Answer
S <- rolldie(1, makespace = TRUE)
Prob(S, X1 < 5)
```

2. How many outcomes are there in the sample space of an experiment in which we
   toss three dice?
```{r}
three_dice <- rolldie(3, makespace = TRUE)
nrow(three_dice)
```

3. Continuing with the three dice rolling experiment:
   a. what is the probability of getting a total of the three dice equal to 5, 6
      or 7?
```{r}
three_dice <- addrv(space = three_dice, FUN = sum, invars = c("X1", "X2", "X3"), name = "Total")
total_equals_5_6_7 <- subset(three_dice, Total >= 5 & Total <= 7)
nrow(total_equals_5_6_7) / nrow(three_dice)

#Answer
Prob(three_dice, Total >= 5 & Total <= 7)
```
   b. how many outcomes lie within this event total_equals_5_6_7 (i.e. how large
      is the event space)?
```{r}
nrow(total_equals_5_6_7)
```
   c. We worked out the size of the sample space for this experiment in question
      2. How do the sizes of the sample and event spaces relate to the
      probability from part i?
```{r, eval=FALSE}
Event space is a subset of sample space.

#Answer
probability from 1 is number of rows in total_equals_5_6_7 / number of rows in
three_dice
```
   d. What assumptions do we apply in answering part iii?
```{r, eval=FALSE}
All outcomes have equal probability of happening.
```

4. Five chairs are in a room along with five people of differing height. The
   people sit down randomly on the chairs. What is the probability that they sit
   in order of decreasing height, left to right?
```{r}
people <- c("shortest", "shorter", "middle", "taller", "tallest")
total <- permutations(n = 5, r = 5, v = people, repeats.allowed = FALSE)
1 / nrow(total)
```

5. I roll six dice: 
   a. what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on
      the dice, left to right?
```{r}
six_dice_perm <- permutations(n = 6, r = 6, repeats.allowed = TRUE)
1 / nrow(six_dice_perm)

#Answer
six_dice <- rolldie(6, makespace = TRUE)
Prob(six_dice, isin(six_dice, c(6, 5, 4, 3, 2, 1), ordered = TRUE))
```
   b. what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1
      on the dice regardless of order?
```{r}
six_dice_comb <- permutations(n = 6, r = 6, repeats.allowed = FALSE)
nrow(six_dice_comb) / nrow(six_dice_perm)

#Answer
Prob(six_dice, isin(six_dice, c(6, 5, 4, 3, 2, 1), ordered = FALSE))
```

6. If I draw a single card from a 52-card deck, and it is black, what is the
   probability that its suit is spades?
```{r}
0.5

#Answer
cards <- cards(jokers = FALSE, makespace = TRUE)
cards <- addrv(cards, FUN = function(suit) {suit == "Club" | suit == "Spade"},
        invars = c("suit"), name = "black")

prob_spades_and_black <- Prob(cards, suit == "Spade" & black == TRUE )
prob_black <- Prob(cards, black == TRUE )

prob_spades_given_black <- prob_spades_and_black / prob_black
prob_spades_given_black
```

7. Eight patients: Alice, Bob, Carmen, Dinesh, Ella, Fergus, Gianna and Henry
   are waiting to see a doctor, but only five appointment slots are left today.
   a. In how many different orders can the doctor see patients today?
```{r}
patients <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna"
        , "Henry")
patient_order <- permutations(n = 8, r = 5, v = patients,
        repeats.allowed = FALSE)
nrow(patient_order)
```
   b. What is the probability of Gianna and Danesh both being seen today?
```{r}
p_gianna <- as.data.frame(patient_order)
names(p_gianna) <- c("x1", "x2", "x3", "x4", "x5")
p_gianna <- p_gianna[p_gianna$x1 == "Gianna" | p_gianna$x2 == "Gianna"
        | p_gianna$x3 == "Gianna" | p_gianna$x4 == "Gianna"
        | p_gianna$x5 == "Gianna", ]

p_dinesh <- as.data.frame(patient_order)
names(p_dinesh) <- c("x1", "x2", "x3", "x4", "x5")
p_dinesh <- p_dinesh[p_dinesh$x1 == "Dinesh" | p_dinesh$x2 == "Dinesh"
        | p_dinesh$x3 == "Dinesh" | p_dinesh$x4 == "Dinesh"
        | p_dinesh$x5 == "Dinesh", ]

n_gianna_and_dinesh <- intersect(p_gianna, p_dinesh)

nrow(n_gianna_and_dinesh) / nrow(patient_order)

#Answer
patient_order <- probspace(patient_order)
Prob(patient_order, isin(patient_order, c("Gianna", "Dinesh"), ordered = FALSE))
```
   c. What is the probability of Gianna being seen before Dinesh today?
```{r}


#Answer
Prob(patient_order, isin(patient_order, c("Gianna", "Dinesh"), ordered = TRUE))
```
   d. Carmen and Henry have now been triaged as high priority and will be seen
      in the first two available slots, although their order hasn’t yet been
      determined. In how many different orders can the patients now be seen?
```{r}
patients <- c("Alice", "Bob", "Dinesh", "Ella", "Fergus", "Gianna")
patient_order <- permutations(n = 6, r = 3, v = patients,
        repeats.allowed = FALSE)
nrow(patient_order) * 2
```
      
8. If order is not significant, how many ways are there to select a 5 student
   quiz team from a group of 8 students?
```{r}
team <- combinations(n = 8, r = 5, repeats.allowed = FALSE)
nrow(team)
```

9. How would your answer above change if a team captain had to be selected for
   each team?
```{r}
team <- combinations(n = 7, r = 4, repeats.allowed = FALSE)
nrow(team) * 8
```

10. The following data from a sample of 120 families shows the record of
    university attendance by mothers and their eldest sons.
    - in 32 families, both the mother and son attended university; 
    - in 31 families, neither the mother nor the son attended university 
    - in 22 families, the mother attended university while the son did not 
    - in 35 families, the son attended university while the mother did not.
    
    Arrange the data above in a convenient dataframe and answer the following
    questions:
    ```{r}
attendance <- data.frame(mother_yes = c(32, 22), mother_no = c(35, 31))
attendance <- cbind(attendance, rowSums(attendance))
attendance <- rbind(attendance, colSums(attendance))
rownames(attendance) <- c("son_yes", "son_no", "sum")
colnames(attendance) <- c("mother_yes", "mother_no", "sum")
```
    a. What is the probability that a son attended university given that his 
       mother attended university?
```{r}
attendance["son_yes", "mother_yes"] / attendance["sum", "sum"]
```
    b. What is the probability that a son attended university given that his 
       mother did not attend university?
```{r}
attendance["son_yes", "mother_no"] / attendance["sum", "sum"]
```
    c. Is attending university by the son independent of whether his mother
       attended university?
```{r}
p_son_attends <- attendance["son_yes", "sum"] / attendance["sum", "sum"]
p_mother_attends <- attendance["sum", "mother_yes"] / attendance["sum", "sum"]

p_son_attends * p_mother_attends
```
