---
title: "R Notebook"
output: html_notebook
---

Beer 
- A dataset with the brand, brewer, alcohol percentage, calories and grams of carbohydrates for 172 beers.

Temp
- A matrix which contains the maximum temperature for each month in Scotland over 106 years (1910 from 2015). Each row corresponds to a year and each column to a month (January to December).

Game of Thrones
- Data on about the book ‘A Game of Thrones’, including names and genders for all the characters.
                        
```{r}
library(CodeClanData)
library(purrr)
```

Correct errors in datasets.
```{r}
beer$calories <- as.numeric(beer$calories)
```

Give datasets more appropriate column/row names if needed.
```{r}
rownames(temp) <- c(1910:2015)
```

================================================================================

1. Find at least two interesting facts for each dataset.

beer

Which brewery has the highest and lowest, mean percent alcohol, calories and
carbohydrates?
```{r}
#subset columns and aggregate over the brewer
beer_columns_to_keep <- c("percent", "calories", "carbohydrates")
aggregated_beer <- aggregate(beer[ , beer_columns_to_keep], 
        by = list(beer$brewer), FUN = mean)

#order aggregated data by the 3 columns
aggregated_beer[order(aggregated_beer$percent), ]
aggregated_beer[order(aggregated_beer$calories), ]
aggregated_beer[order(aggregated_beer$carbohydrates), ]

```

What beers have the lowest and highest percent alcohol, calories and
carbohydrates?
```{r}
beer[beer$percent == min(beer$percent), c("brand", "brewer", "percent")]
beer[beer$percent == max(beer$percent), c("brand", "brewer", "percent")]
beer[beer$calories == min(beer$calories), c("brand", "brewer", "calories")]
beer[beer$calories == max(beer$calories), c("brand", "brewer", "calories")]
beer[beer$carbohydrates == min(beer$carbohydrates), c("brand", "brewer", "carbohydrates")]
beer[beer$carbohydrates == max(beer$carbohydrates), c("brand", "brewer", "carbohydrates")]
```

================================================================================
temp

What are the coldest and hottest months in the dataset?
```{r}
#Coldest
position <- which(temp == min(temp), arr.ind = TRUE)
paste("The coldest temperature was",
      temp[position[[1]], position[[2]]],
      "in",
      colnames(temp)[position[[2]]],
      rownames(temp)[position[[1]]]
)
```

```{r}
#Hottest
position <- which(temp == max(temp), arr.ind = TRUE)
paste("The warmest temperature was",
        temp[position[[1]], position[[2]]],
        "in",
        colnames(temp)[position[[2]]],
        rownames(temp)[position[[1]]]
)
```

What are the mean coldest and hottest years on record?
```{r}
yearly_temp <- rowMeans(temp)
paste("The year with the lowest average temperature is",
        names(yearly_temp[min(yearly_temp)]),
        "at",
        round(min(yearly_temp), digits = 2)
)
paste("The year with the highest average temperature is",
        names(yearly_temp[max(yearly_temp)]),
        "at",
        round(max(yearly_temp), digits = 2)
)
```

Plot of minimum and maximum temperatures by year
```{r}
plot(rownames(temp), apply(temp, 1, min), main = "Minimum temperature by year",
        xlab = "Year", ylab = "Temperature in degrees")

plot(rownames(temp), apply(temp, 1, max), main = "Maximum temperature by year",
        xlab = "Year", ylab = "Temperature in degrees")
```

================================================================================

game_of_thrones

How many male and female characters are in the book?
```{r}
paste("There are",
        sum(map(game_of_thrones$characters, "gender") == "Male"),
        "male characters and",
        sum(map(game_of_thrones$characters, "gender") == "Female"),
        "female characters in",
        game_of_thrones$name
)
```






























