---
title: "R Notebook"
output: html_notebook
---

```{r}
library(zoo)
library(xts)
library(lubridate)
library(tseries)
library(forecast)
library(tibbletime)
library(timetk)
library(tidyverse)
```

MVP

Question 1

Load in the sunspots data and check it is a time series. Get the start, end,
periodicity, frequency and cycle information. Get the start and end times,
periodicity, frequency, and anything else you need to understand your data.
```{r}
data(sunspots)
start(sunspots)
end(sunspots)
frequency(sunspots)
cycle(sunspots)
sunspots
```

Question 2

Write an initial description of your data. Give enough detail that you could use
it as a description for a data dictionary or for another analyst to follow.
```{r}
# Data is a time series matrix containing the mean relative sunspot numbers for
# each month from 1749 to 1983 inclusive.
```

Question 3

Calculate the rolling average of your sunspots data, and plot it. Hint: You’ll 
need to choose the window you want to average over to make sure it’s 
representative of this particular time series
```{r}
rolling_average <- rollapply(sunspots, width = 12, align = "right", FUN = mean,
        na.rm = TRUE)

sunspots_cbind <- cbind(sunspots, rolling_average)
plot(sunspots_cbind)
```

Question 4

Decompose the time series and look at the different components. Make sure you 
use the right type of decomposition. Then take a look at your different 
components. What does it all tell you? Hint: you might need to subset some of 
your data in order to see patterns more clearly
```{r}
sunspots_subset <- ts(sunspots[1:192], frequency = 12, start = 1749)
plot(decompose(sunspots_subset, type = "multiplicative"))
# trend is varied
# strongly seasonal
# no clear pattern of random noise
```

Question 5

Check if your data is stationary using the appropriate plots. Do you have 
stationary data? If no, make the data stationary.
```{r}
plot(aggregate(sunspots, FUN = mean))
boxplot(sunspots ~ cycle(sunspots))
# year on year trend varies wildly
# minimal seasonal effect
# not stationary

sunspots_log <- log(sunspots)
sunspots_detrend <- diff(sunspots_log)
plot(sunspots_detrend)

adf.test(sunspots_detrend, alternative = "stationary", k = 0)
# doesn't work because sunspots_detrend has "inf" and "NaN' values in it.
```

Question 6

Now we have our data, choose your ARIMA model parameters. Create ACF and PACF 
plots to check, and write a summary of what you have found.
```{r}
acf(sunspots_detrend)
pacf(sunspots_detrend)
# won't work as it builds on 5
```

Question 7

Fit an ARIMA model that predicts the sunspots for the next 20 years. Plot the 
data, and have a look at your forecast. Does it look like a good forecast or 
good fit?
```{r}
fit <- arima(sunspots_log, c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 240))
# lso won't work as it builds on 5
```

Question 8

Problem solving: Your model isn’t predicting that well. What are some reasons 
you can think for this?
```{r}
# seasonality is incorrect
```

Question 9

Problem solving:

In the present case, sunspots have a cycle of length 11 years. To know this, 
you’d have to know something about sunspots. You can find this here. The 
sunspots data are a monthly time series. Thus, the implicit seasonality of 
sunspots is 12 (months), not 11×12=132 (months).

ARIMA and auto.arima() were never built to automatically detect a seasonal cycle
whose length is not pre-specified. It is not overly surprising it does not see 
that it should do 11 seasonal differences to model a seasonality that repeats 
every 11 cycles of its prespecified frequency.

So, the first order of business would be to specify that seasonal cycles are 
indeed of length 132 (i.e. 1112). Then you’ll need to use this seasonally 
adjusted data in your model, and include a seasonality parameter into your 
arima model (try ?auto.arima) to show how to do this. Hint, it involves setting
your D parameter = 1*. Then you can plot your data and predict the next 20 
years. Is this a better fit?
```{r}
# also builds on 5 so whatever goes here won't work either.
```

Extensions

Question 1

The dataset, sunspot.month is a ts class, rather than a classic tidy tibble. 
Using your knowledge of tidyverse and ts objects, convert the sunspot.month data
to a tidy data set using the tk_tbl() function from timetk package. Using this 
instead of as.tibble() (from the tibble package) is better because it 
automatically preserves the time series index.

Then, convert the index to date using lubridate::as_date() and then change to a 
tbl_time object (from the tibbletime package).

Then summarise the median value of sunspots in the year 1980. Hint: you’ll have 
to combine your knowledge of how to filter and summarise dates and times in 
tidyverse to do this.
```{r}
sunspot_month_tibble <- tk_tbl(data = sunspot.month, rename_index = "date")

sunspot_month_tibble$date <- lubridate::as_date(sunspot_month_tibble$date)

sunspot_month_tibble <- tbl_time(sunspot_month_tibble, index = date)

sunspot_month_tibble %>%
        filter(date >= "1980-01-01" & date <= "1980-12-01") %>%
        summarise(median = median(value))
```

Question 2

Get and load the package ‘xts’ and all required packages. Create the objects 
‘measurment’ and ‘dates’ like below.

measurement <- rep(sin(seq(0,10,length.out = 90)),4) + rnorm(90*4)
dates <- seq(as.Date("1987-01-01"), as.Date("1987-12-26"), "day")

Use the two objects to create an xts time series (mytimeseries) ordered by 
dates. Check the class, structure, number of years, months and quarters. Get the
core data and index as well, and check these are matrix and index data.

Select all of the August to September data in your xts object. Plot this new xts
time series.Use apply.monthly from xts to get a monthly mean on the time series.
Finally, get a monthly plot.
```{r}
measurement <- rep(sin(seq(0, 10, length.out = 90)), 4) + rnorm(90 * 4)
dates <- seq(as.Date("1987-01-01"), as.Date("1987-12-26"), "day")

mytimeseries <- xts(x = measurement, order.by = dates)
class(mytimeseries)
str(mytimeseries)

ep_y <- endpoints(mytimeseries, on = "years")
ep_m <- endpoints(mytimeseries, on = "months")
ep_q <- endpoints(mytimeseries, on = "quarters")

xts_core <- coredata(mytimeseries)
xts_index <- index(xts_core)
class(xts_core)
class(xts_index)

plot(mytimeseries["19870801/19870930"])
apply.monthly(mytimeseries, FUN = mean)
plot(apply.monthly(mytimeseries, FUN = mean))
```
