---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(ggplot2)
```

4.1. 

Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart 
showing the sources of revenue across the two years in the dataset.
```{r}
ggplot(qb_revenue_breakdown) +
        aes(x = Year, y = Revenue, fill = Product) +
        geom_bar(stat = "identity") +
        labs(title = "Revenue per Source by Year\n")
```

Make a line chart showing monthly sales of the “flagship product” - the KwikBit 
Unit1 - over the last year. 
```{r}
ggplot(qb_monthly_sales[qb_monthly_sales$Cashflow == "Kwikbit Unit 1 Sales", ]) +
        aes(x = Date, y = Amount) +
        geom_line() +
        geom_point() +
        labs(title = "Sales by Date\n")
```

Make a line chart showing monthly revenue and costs over the last year.
```{r}
ggplot(qb_monthly_sales[qb_monthly_sales$Cashflow != "Kwikbit Unit 1 Sales", ]) +
        aes(x = Date, y = Amount, colour = Cashflow) +
        geom_line() +
        labs(title = "Revenue and Costs by Date\n")
```

4.2.

Show annual sales of personal fitness trackers over the last 5 years broken down
by company as a ribbon plot.
```{r}
ggplot(qb_competitors) +
        aes(x = Year, y = Revenue, fill = Company) +
        geom_area(alpha = 0.25) +
        labs(title = "Annual Revenue by Company\n")
```

Now show the sales from the 5 competitors as a line graph. Include an extra 
layer that shows the data points used to make the lines.
```{r}
ggplot(qb_competitors) +
        aes(x = Year, y = Revenue, colour = Company) +
        geom_line() +
        geom_point() +
        labs(title = "Revenue by Year\n")
```

5.

Try out different ways of plotting these three datasets. Which graphs do you 
think are particularly effective at showing QikBit’s success?

qb_revenue_breakdown
- bar makes most sense since there's only 2 points for year for each product.

line chart
```{r}
ggplot(qb_revenue_breakdown) +
        aes(x = Year, y = Revenue, group = Product, colour = Product) +
        geom_line() +
        labs(title = "Revenue per Product by Year\n")
```

```{r}
ggplot(qb_revenue_breakdown) +
        aes(x = Product, y = Revenue, fill = Year) +
        geom_bar(stat = "identity") +
        labs(title = "Revenue per Year by Product")
```

qb_monthly_sales

```{r}
ggplot(qb_monthly_sales) +
        aes(x = Date, y = Amount, fill = Cashflow) +
        geom_bar(stat = "identity") +
        labs(title = "Amount per Cashflow by Date\n")
```

```{r}
ggplot(qb_monthly_sales) +
        aes(x = Cashflow, y = Amount, fill = Cashflow, colour = Date) +
        geom_bar(stat = "identity") +
        labs(title = "Amount per Date by Cashflow\n")
```

qb_competitors

```{r}
ggplot(qb_competitors) +
        aes(x = Year, y = Revenue, fill = Company) +
        geom_area(position = "fill", alpha = 0.25) +
        labs(title = "Relative composition of Competitor Revenue by Year\n")
```
