---
title: "R Notebook"
output: html_notebook
---

MVP

```{r}
library(tidyverse)
library(readxl)
library(stringr)
library(lubridate)
```

Load in the code_clan_tweets.csv. Find the number of rows, columns, and lists of
all the variable names.
```{r}
code_clan_tweets <- 
        read_csv("~/de1_classnotes/week_06/day_5/5_Weekend_Homework/data/code_clan_tweets.csv")

dim(code_clan_tweets)
names(code_clan_tweets)
```

First, we’re going to summarise the number of likes CodeClan tweets have. Create
a boxplot to check for outliers.
```{r}
boxplot(code_clan_tweets$favorite_count)
```

Summarise the number of likes (stored in favorite_count) that CodeClan tweets
have got. Don’t summarise when it was a quoted tweet (is_quote variable).
```{r}
summary(code_clan_tweets[, "is_quote" != FALSE]$favorite_count)
```

Summarise the mean number of retweets (retweet_count), by the type of platform
that was used to tweet (source).
```{r}
code_clan_tweets %>%
        group_by(source) %>%
        summarise(mean(retweet_count))
```

Count the number of likes by media type, and arrange them from most likes to
least.
```{r}
code_clan_tweets %>%
        group_by(media_type) %>%
        summarise(count_likes = sum(favorite_count))
```

Find the mean number of characters a CodeClan tweet contains.
```{r}
mean(code_clan_tweets$display_text_width)
```

Convert the dates in the created_at variable into ISO format, and store them in
a new datetime variable. Get the months and store them in a new variable called
month.
```{r}
code_clan_tweets <- code_clan_tweets %>%
        mutate(datetime = dmy_hm(created_at)) %>%
        mutate(month = month(datetime))
```

Using your new month column, count the number retweets codeclan got in May vs 
April.
```{r}
code_clan_tweets %>%
        group_by(month) %>%
        summarise(retweets = sum(retweet_count))
```

The code_clan_info.csv contains url and tweet info. Load this in, and join it to
the code_clan_tweets data, so that you have a tweet url for wherever you have a
tweet.
```{r}
code_clan_info <- 
        read_csv("~/de1_classnotes/week_06/day_5/5_Weekend_Homework/data/code_clan_info.csv")
```

```{r}
combined <- left_join(code_clan_tweets, code_clan_info, by = "tweet_id")
```

From your new joined data, create a variable which has all the hashtags in 
lowercase for analysis.
```{r}
combined <- combined %>%
        mutate(lower_hashtag = str_to_lower(hashtags))
```

Some tweets have more than one hashtag, denoted by the c() expression at the 
start of the string. Use the substr and str_detect functions to create a tibble
where the first letter of the string begins with a c.
```{r}
combined %>%
        filter(str_detect(combined$lower_hashtag, pattern = "c\\(") == TRUE)
```

Use the str_extract function to find all cases where a tweet mentions edinburgh
anywhere in it. How many mentions of Edinburgh are there in CodeClan’s tweets?
```{r}
sum(!is.na(str_extract(combined$text, pattern = "[eE]dinburgh")))
```

Use str_extract_all with a regular expression to find out which users CodeClan
have been tweeting. Hint: think about all the different characters which could
be in a username
```{r}
users <- str_extract_all(combined$text, pattern = "@\\w+", simplify = TRUE)

users[users[ , 1] != "", ]
```

Extensions

codeclan_info has tweet url (status_url) stored in a string. Save the numeric
substring part of the string in a new variable called status_url_number
```{r}
code_clan_info <- code_clan_info %>%
        mutate(status_url_number = str_extract(status_url, pattern = "[0-9]{19}"))
```

Use the str_replace function to replace the url numbers in the status_url_number
string with a the word HIDDEN_URL
```{r}
code_clan_info$status_url <-
        str_replace(code_clan_info$status_url, code_clan_info$status_url_number, "HIDDEN_URL")
```

Use str_detect to see which tweets don’t include a shortened link
(https://t.co/**********)
```{r}
code_clan_tweets[str_detect(code_clan_tweets$text, pattern = "https:\\/\\/t.co\\/", negate = TRUE) == TRUE, ]
```
