---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readxl)
library(ggplot2)
```

1.

Load in the dataset and call it drinks_content, eyeball it by printing it out
(first 5 rows, last 5 rows, and then all of the data) and find out the 
dimensions (number of rows/columns) and variable names.
```{r}
filename <- "~/de1_classnotes/week_06/day_1/6_dplyr_homework/data/starbucks_drinkMenu_expanded.csv"

drinks_content <- read_csv(filename)

head(drinks_content, n = 5)
tail(drinks_content, n = 5)
drinks_content

dim(drinks_content)
names(drinks_content)
```

Calculate some quick summary statistics to check the mean, the variance, and the
normality of this variable.
```{r}
summary(drinks_content$Calories)

ggplot(drinks_content) +
        aes(x = Calories) +
        geom_histogram()
```

Check if you have any outliers in the Calories variable by creating a boxplot.
Then get the actual values of any outliers you have. Finally remove the outliers
and save the new tibble as drinks_content_nooutlier.
```{r}
boxplot(drinks_content$Calories)

outliers <- boxplot(drinks_content$Calories, plot=FALSE)$out

drinks_content_nooutliers <- 
        drinks_content[-which(drinks_content$Calories %in% outliers), ]
```

Select the variables beverage_category, beverage, beverage prep and calories
from the data (drinks_content_nooutlier), and assign it to a new tibble called
drinks. Since we are interested in the calorie content, check if there are any
NA values in the data, and drop them if there are.
```{r}
drinks <- select(drop_na(drinks_content_nooutliers), Beverage_category:Calories)
```

Filter the data so we only take “classic espresso drinks”, and save this in a 
new tibble called espresso_drinks.
```{r}
espresso_drinks <- filter(drinks, Beverage_category == "Classic Espresso Drinks")
```

Create a new tibble called drink_calories which contains a variable called 
calorie_diff. calorie_diff should store the difference between 135 calories 
(135 calories = 10 cubes of sugar!) and the calories in each drink.
```{r}
drink_calories <- mutate(espresso_drinks, calorie_diff = 135 - Calories)
```

Create a new tibble called drinks_grouped where you group your data by the type
of beverage prep. Then summarise the mean calories in each drink (by group) in a
variable called mean_cal, and save it to drinks_summary. Finally arrange this
summary data in descending order of mean calories.
```{r}
drinks_grouped <- group_by(drink_calories, Beverage_prep)
drinks_summary <- summarise(drinks_grouped, mean_cal = mean(Calories))
arrange(drinks_summary, desc(mean_cal))
```

Finish up by using the %>% operator to put all the answers you’ve got from 
questions 4-7 into one pipe. You don’t need to include the check for NA values 
in this, as you’d typically check that before you start doing any analysis.
```{r}
drinks_content %>%
        drop_na() %>%
        select(Beverage_category:Calories) %>%
        filter(Beverage_category == "Classic Espresso Drinks") %>%
        mutate(calorie_diff = 135 - Calories) %>%
        group_by(Beverage_prep) %>%
        summarise(mean_cal = mean(Calories)) %>%
        arrange(desc(mean_cal))
```

2.

Use the drink_calories data, and for each drink, use the min_rank function to
find the two drinks (Beverage) with most Calories. Save this in a new tibble 
called most_calories.
```{r}
most_calories <- drink_calories %>%
        mutate(Rank = min_rank(Calories)) %>%
        arrange(desc(Rank)) %>%
        top_n(2)
```

For each drink in the drinks_grouped data, find all drinks which more calories
than the average drink. Save this in a new tibble called above_average_calories.
```{r}
above_average_calories <- drinks_grouped %>%
        filter(Calories > mean(drinks_grouped$Calories))
```

Within each drink group, rank each beverage by the number of calories. Save this
ranking in a new column called ranking. Save the new output in a new tibble 
called drinks_ranked.
```{r}
drinks_ranked <- drinks_grouped %>%
        group_by(Beverage) %>%
        mutate(ranking = min_rank(Calories))
```

Using the drinks_grouped data, apply the cume_dist function to get the top 25% 
of Calorie drinks within each group. Save this in a new tibble called 
drinks_distribution.
```{r}
drinks_distribution <- drinks_grouped %>%
        filter(cume_dist(desc(Calories)) < 0.25)
```
