---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)
```

MVP

Use the stock prices data from the CodeClanData: IBM_stock_price and 
JNJ_stock_price
```{r}
IBM_stock_price
JNJ_stock_price
```

Your JNJ data is in wide format. Reshape it so it is in long format. Create two
columns: one called date and one called jnj_open (as it is open stock prices).
Save it in a new tibble called JNJ_stock_price_gathered.
```{r}
JNJ_stock_price_gathered <- gather(JNJ_stock_price,
        key = date,
        value = jnj_open,
        "12/04/17":"13/03/17"
)
```

Your IBM data has a variable called agents in it, which contains the initials of
the two staff working. Separate out this column into two: agent1 and agent2.
Save the output in a new tibble called IBM_agents.
```{r}
IBM_agents <- separate(IBM_stock_price,
        col = Agents,
        into = c("agent1", "agent2"),
        sep = "\\/"
)
```

Use the unite function to unite the Agent ID columns (ID1,ID2) with the agent
initials. Use a colon as a separator. Hint: you might need to use a pipe to do 2
unite functions. Select only the agent variables and save it in a tibble called
IBM_agent_data.
```{r}
IBM_agent_data <- IBM_agents %>%
        unite(col = agent1, c("ID1", "agent1"), sep = ":") %>%
        unite(col = agent2, c("ID2", "agent2"), sep = ":")

```

Your JNJ data only has data for open stock. Therefore first thing to do is
create a new tibble called IBM_data, which selects only the date and the open
stock data from the IBM_stock_data tibble. Once you have that, use a full join
to join the IBM_data and JNJ_data tibbles. Save it in a new tibble called
open_stock_data.
```{r}
IBM_data <- IBM_stock_price %>%
        select(date, open)

open_stock_data <- full_join(IBM_data, 
        JNJ_stock_price_gathered, 
        by = "date"
)
```

Write a for loop which calculates the mean of each variable in the open_stock
dataset. Save the output in a vector called stock_mean_data. 
```{r}
stock_mean_data <- numeric(length = length(open_stock_data) -1 )

for (column in 2:length(open_stock_data)) {
        stock_mean_data[[column - 1]] <- mean(open_stock_data[[column]])
}
```

Now do the same calculation with the appropriate map function.
```{r}
map_dbl(open_stock_data[ , -1], mean)
```

Extension

Write a loop which calculates the length of each variable in open_stock
```{r}
for (column in 1:length(open_stock_data)) {
        print(length(open_stock_data[[column]]))
}
```

Write a loop which prints the type of each variable in open_stock
```{r}
for (column in 1:length(open_stock_data)) {
        print(class(open_stock_data[[column]]))
}
```

Use the map function to turn your date column in stock_data into datetimes.
```{r}
open_stock_data[ , 1] %>%
        map(as.Date, format = "%d/%m/%y")
```

Use the map function to calculate the median of the stock price.
```{r}
open_stock_data[ , -1] %>%
        map_dbl(median)
```

Calculate summary stats for all the numeric variables.
```{r}
open_stock_data[ , -1] %>%
        map(summary)
```
